[dcpo_demsupport]

### 2020-06-16 paper/dcpo_demsupport.Rmd
clean up

```{r claassen_input_raw}
claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv"),
                                       file = "data/claassen_input_raw.csv")
```

>>>>

```{r claassen_input_raw}
claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv",
                                                                 col_types = "ccccc"),
                                       file = "data/claassen_input_raw.csv")
```
